---
title: "COVID-19 in Lubbock"
output: html_notebook
---
## What is this?
This is an R notebook to help visualize the numbers regarding COVID-19 in Lubbock, TX. I've been keeping this data in JSON format as press releases come out from the [City of Lubbock](https://twitter.com/cityoflubbock). The code for this notebook can be found here -> [https://github.com/jreina/lubbock-covid](https://github.com/jreina/lubbock-covid).

Last Updated: `r Sys.time()`

```{r, results='hide', message=FALSE, warning=FALSE}
library('jsonlite')

cases <- as.data.frame(fromJSON("./data/cases.json"))
dates <-as.Date(paste(cases$date, cases$time), "%m/%d/%Y %H:%M")
cases$difference = c(0, diff(cases$confirmed))
cases <- cases[, c(1, 3, 8, 5, 6, 7)]
```

## Active cases vs recoveries by date
```{r, results='hide', message=FALSE, warning=FALSE}
plot.new()

plot(range(dates), range(cases$confirmed))

legend('topleft', legend = c('Active cases', 'Recoveries'), col = c('red', 'blue'), lty = 1, lwd = 2.5)

lines(x = dates, y = cases$confirmed - cases$recovered - cases$deaths, lwd = 2.5, col = 'red', lty = 1)
lines(x = dates, y = cases$recovered, lwd = 2.5, col = 'blue', lty = 1)
```

## New confirmed cases by date
```{r, results='hide', message=FALSE, warning=FALSE}
plot.new()

plot(range(dates), 
     range(cases$difference), lwd = 1, col = 'blue', lty = 1)

legend('topleft', legend = c('New cases'),
       col = c('blue'), lty = 1, lwd = 2.5)

lines(x = dates, y = cases$difference, lwd = 2.5, col = 'blue', lty = 1)
```

## Cumulative statistics by date

```{r, results='hide', message=FALSE, warning=FALSE}
plot(range(dates), 
     range(cases$confirmed),
     type = 'n', 
     xlab = 'Date', 
     ylab = 'Count')

lines(dates, cases$confirmed, col = "black", lwd = 2.5)
lines(dates, cases$recovered, col = "green", lwd = 2.5)
lines(dates, cases$deaths, col = "red", lwd = 2.5)
lines(x = dates, y = cases$difference, lwd = 1, col = 'purple', lty = 2)

legend('topleft', legend = c('Confirmed', 'Recovered', 'Deaths', 'Difference'), 
       col = c('black', 'green', 'red', 'purple'), lty = c(1, 1, 1, 2), lwd = c(2.5, 2.5, 2.5, 1))
```

## Data

```{r, results='asis', message=FALSE, warning=FALSE}
library(xtable)
print(xtable(cases), type = "html")
```

### Disclaimer
This data likely varies from official data since it is based on press releases instead of aggregated health department data from the State of Texas. This data is provided purely for informational purposes.
